### 2016-03-11 manuscript.Rnw
caught missing newline

<<get_cats, purl=FALSE, fig.cap="Tree from \\citealt{Johnson2006} obtained from OTL">>=
cat_studies <- studies_find_studies(property = "ot:focalCladeOTTTaxonName",
                                    value = "Felidae", exact = TRUE)cat_studies
@

>>>>

<<get_cats, purl=FALSE, fig.cap="Tree from \\citealt{Johnson2006} obtained from OTL">>=
cat_studies <- studies_find_studies(property = "ot:focalCladeOTTTaxonName",
                                    value = "Felidae", exact = TRUE)
cat_studies
@
